\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-18 paper.tex
Contribution Rachid - Execution control

%The novelty of our contribution here is the interleaving of a semantic-aware
%architecture designed for autonomy with human-aware decisional components. To
%our knowledge, no other robotic architecture covers in depth those two
%perspectives.
%
%The Ke Jia project~\cite{Chen2010} is maybe one of the closest
%approach. It integrates on a mobile platform a knowledge representation language
%with natural language processing, task planning and motion planning. Default and
%non-monotonic reasoning has been especially researched within the Ke Jia project
%for symbolic task planning~\cite{Ji2011} and underspecified natural language
%processing. The Ke Jia robot has been demonstrated in several tasks involving human-robot
%interaction with natural language. These tasks include a task with multiple
%\emph{pick \& carry} that are globally optimised, naive physics reasoning via
%taught rules or more complex scenarios with the robot delivering drinks, taking
%into account changing and mutually exclusive preferences of users.
%
%Also notable, Beetz et al.~\cite{Beetz2010} proposes a cognitive architecture
%called \textsc{CRAM} (Cognitive Robot Abstract Machine) that deeply integrates
%with \textsc{KnowRob}~\cite{Tenorth2009a}, a knowledge processing framework
%based on Prolog. Its underlying storage is based on an OWL ontology, derived
%from \textsc{OpenCyc}. \textsc{CRAM} and \textsc{KnowRob} have been demonstrated
%on several real-world scenarios, where natural language recipes extracted from
%the Internet had to be translated into plans and executed in a kitchen
%environment, perceived and rebuilt on-line by the robots. This architecture has
%however not been deployed in many scenarios involving human-robot interactions.
%

>>>>

One of the main role of {\sc Shary} is to control the elaboration and execution
of shared plans~\cite{Grosz1996,Clark1996,Kemp2007}. This means essentially
contex-based refinement and robot actions execution as well as monitoring of
those achieved by its human partner~\cite{Breazeal2003}. The challenge is to
build such abilities in a generic way, and to provide several levels of
parametrization allowing to adapt to various environments, and various levels of
involvement of the robot ranging from teammate behavior to assistant or
proactive helper.  Depending on this, the robot controller invokes the various
human-aware planners and will react to events detected at ORO level.

SHARY’S originality, as a supervision system, lies in its ability to take into
account not only the task achievement but also communication and monitoring
needed to support interactive task achievement ~\cite{Rich1997,Sidner2005} in a
flexible way. SHARY allows to link action execution to more or less elaborated
“communication policies” in order to produce signals towards the human and to
react to human action.

A communication act is the central notion in the formalism. It plays the role of
transition condition. Consequently, a communication act represents an
information exchange between the two agents. This exchange can be realized
through dialog or by an expressive motion or a combination of the two. It
enables each agent to communicate his belief about the task to be realized in
order to share mutual knowledge and to synchronyze their activities.  This is
done through real-time task-based situation assessment achieved by the
combination of SPARK monitoring processes and ORO inference mechanisms
\cite{fiore2014}.
